Mirror, mirror on the wall. Which's the best match of them all?

### 2023-12-06 PNAS/index.Rnw
Alicia updates

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor} % colors
\newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
\newcommand{\hh}[1]{{\textcolor{ForestGreen}{#1}}}
\templatetype{pnasbriefreport}
%\templatetype{pnasbriefreport} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\title{Mirror, mirror on the wall. Who's the best match of them all?}

@@

\begin{abstract}
Wires have striations left from the cutting process; as in other forms of toolmark analysis, these striae are used to connect the wire to the tool used. In this paper, we show that the process of wire comparison introduces complexities not present in better-investigated forensic toolmark areas such as bullets, as wire comparison inherently requires multiple distinct comparisons, increasing the expected false positive rate. We call attention to the multiple comparison problem in wire examination and relate it to other situations in forensics that involve multiple comparisons, such as database searches.
\end{abstract}

@@

\dropcap{I}n forensic evidence a single conclusion is often based on  many comparisons, either implicitly or explicitly.
Multiple comparisons are a persistent problem when developing statistical methods for scientific problems \citep{benjaminiControllingFalseDiscovery1995}.
Researchers have been focusing on building up databases to develop algorithms for objective evidence comparisons.
\svp{Then, the algorithms facilitate} searches across (vast) databases, reporting the best $N$ matches to a particular piece of evidence.
This raises the critically important problem of close non-matches\citep{pcast}.

@@

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{koehler2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.
Very close non-matches are a direct consequence of a large number of comparisons; they will occur more frequently as databases increase in size and algorithms become more powerful.
% In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.

@@

\svp{Compounding this issue,} algorithms make a large number of comparisons that are not obvious to the user.
The cross-correlation function\citep{vorburgerApplicationsCrosscorrelationFunctions2011} was one of the first quantitative measures proposed in response to the NAS report \citep{nas2009}, and is used in many pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity.
Finding the best alignment requires implicitly sliding one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source while keeping track of the value of a similarity measure.
This mirrors the forensic examination process, as examiners visually rotate or align two pieces of evidence under comparison microscopes.
In order to avoid embarrassing false accusations and a further erosion of the public's trust in science, we need to address the problem of multiple comparisons by controlling their effect on false discovery rates.

Here, we consider the multiple comparisons problem that arises from a relatively simple toolmark comparison: matching a cut wire to a wire-cutting tool.
We describe the comparison approach, estimate the (minimal) number of comparisons needed, and discuss how the false discovery rate changes with the number of comparisons involved, using error rates derived from published black-box studies.

@@

A forensics examiner tasked with determining whether a wire in evidence was cut by a specific tool will create one or more blade cuts which can be compared to the cut surface of the wire.
These cuts are made in a sheet of material similar to the wire's composition, and may be performed at multiple angles, as the angle of the tool to the substrate can affect which striations are recorded on the substrate surface.
The blade cuts will then be compared to the wire under a comparison microscope, though eventually, automatic comparison algorithms may also be validated for lab use.
Each side of each blade cut will be compared to each side of the wire; depending on the tool design, there can be between 2 and 4 cutting surfaces in contact with the substrate.

@@

In order to calculate the number of comparisons, we define $\ell$ to be the length of the blade cut, and $d$ to be the diameter of the wire. Without loss of generality, we will assume that the wire is fully covered with striations suitable for comparison; if this is not the case, it is equivalent to changing the value of $d$.
\svp{An illustration of the sliding comparison process is shown in \Cref{fig:wire-blade}.}
At minimum, there must be $\ell/d$ comparisons in order to assess whether one side of the blade cut matches one side of the wire; in this case, the comparisons are independent of each other (conditional on striation patterns) because no overlapping data is used.
Of course, this overlooks the possibility of partial matches and assumes perfect alignment between the diameter of the wire and the portion of the blade used to cut the wire, which is unrealistic.

@@

At a maximum, both the blade and the wire are either digitally scanned at resolution $r$ mm, or visually examined using a microscope with a digital resolution that can be expressed as $r$ equivalent to the digital scan.
In this case, there may be as many as $\ell/r - d/r + 1$ comparisons performed in order to find the optimal alignment between the two samples.
These comparisons are of course highly dependent, as each sequential comparison shares much of the same data with the previous and next comparisons.
% ; such dependency could be expressed via autocorrelation, but we will defer that derivation to a later paper.
\svp{For simplicity}, let us consider the number of comparisons to lie somewhere between \svp{these two estimates}.

Then, we must consider the number of surfaces which must be compared: the wire may have between one and two sets of striae (depending on tool configuration) and there may be between 2 and 4 different blade cut surfaces to examine.
This results in a multiplier of between 2 and 8 comparisons to be conducted to compare the striations on the wire to the striations on the blade cuts.

@@

Let us consider a wire-cutting tool with a 1.5 cm razor blade that meets a cast surface (one such tool is shown in \Cref{fig:tool-pic}); the wire is held against this rectangular cast surface as the blade is pushed into the wire, splitting it in two.
This is a minimal scenario - the wire will have striations from one side of the blade, while the blade itself has two cutting edges, which we will call side A and side B.
The blade cuts of a sheet of aluminum that is 1.5 cm in width thus produce two striated edges corresponding to side A and side B which can be compared to other cuts to assess similarity.

@@

In this example, $\ell = \Sexpr{ell} mm$, $d = \Sexpr{2} mm$, and the minimal number of comparisons between the wire and one blade cut is $\ell/d = \Sexpr{ncomp_min}$.
As there are two blade cuts (side A and side B), the minimal number of comparisons overall is \Sexpr{ncomp_min*2}, and these comparisons are independent.

If the blade cuts and the wire edge are scanned at a resolution of $\Sexpr{res*1000} \mu m$, the resulting digital files will require \svp{approximately $\Sexpr{format(round(ncomp_max/1000)*1000, big.mark=',')}$ comparisons per blade cut; $\Sexpr{format(round(ncomp_max/1000)*2000, big.mark=',')}$ comparisons overall}.
These comparisons are required in order to find the optimal alignment between the wire and the blade cut; they are implicit in the calculation of cross-correlation which is either the first or the only step used to objectively assess the similarity between striated evidence such as bullets, aperture shear, and firing pin impressions.
This problem is not unique to algorithms; an examiner would need to physically align the wire and the blade cut by searching along the length of the cut to visually match striations, performing the same process physically that the algorithm performs computationally.
While these sequential comparisons are of course highly autocorrelated, and we cannot assume sequential independence when calculating the probability of an error, they serve as an upper bound on the number of comparisons which could be performed.

@@

There are two components to a false positive rate: coincidental matches (that is, two pieces of evidence that happen to have similar characteristics but are not from the same source) and human/technical failures \citep[p 50]{pcast}.
In objective disciplines with matching rules, such as DNA, these sources can be distinguished, and when coincidental match rates are very low, human/technical failures make up a large component of the error rate.
However, in toolmark examination, we do not have an objective matching rule; examiners testify based on subjective, individual rules for how much similarity is enough for an identification.
As a result, we cannot separate coincidental match rates from human/technical failures.
<<fpr, include = F>>=
errors <- c(20, 56, 1)
knm <- c(2842, 774, 220)

@@

Compounding this problem, open-set studies of striated comparisons (bullets and firing pin impressions) \citep{bajic2020, mattijssen2021,best2022} suggest \svp{that a starting point for estimating the} false positive rate for these comparisons is between 0.0045 \citep{best2022} and 0.072 \citep{mattijssen2021}; pooling data from these three studies yields a false positive rate of \Sexpr{sprintf("%.2f", fpr)}.

If we begin by considering the multiple comparison problem relative to the $\ell/d$ independent comparisons between a blade cut and a wire, we can calculate the overall false positive rate for all comparisons using $r$, the false positive rate for one comparison, and simple probability. Let $$F_n:=\{\text{at least one false pos. in }n\text{ disjoint comparisons}\}.$$ Then, $P(F_1) = r$, $P(\overline{F_1}) = 1-r$, $P(F_n) = [1-r]^n$, and $P(\overline{F_n}) = 1 - \left[P(\overline{F_1})\right]^n$.
% Using this relationship between $F_n$ and the false positive rate $r$, we can determine what $r$ must be in order to limit $P(F_n)$ to an acceptable level by solving for $r$: $r = 1 - \left[1 - P(F_n)\right]^{1/n}$.
\svp{\Cref{fig:Accuracy} shows $P(\overline{F_n})$ on the y-axis; if we set 90\% as the acceptable probability, we can make 2 comparisons when the single-comparison FPR is 0.05 and 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, we can conduct approximately 5 comparisons while keeping the FPR for all comparisons under 10\%.}

\svp{It is clear that under these constraints, the} accuracy of the aggregate comparison between a wire and a tool becomes questionable, as the number of candidate alignments that must be examined is too high.
Even the most innocuous example we could come up with (small blade, only 2 cutting surfaces, and a relatively large wire) involved a minimum of \Sexpr{2*ncomp_min} completely independent comparisons.
As a result, it seems improbable that a wire comparison made under current protocols (with corresponding error rates) would have an overall accuracy rate which would be reliable enough to be presented at trial.
When we then consider that examiners would make cuts at multiple angles \citep{baikerToolmarkVariabilityQuality2015}, increasing the number of comparisons even in the simple case we have presented here, the probability of a false positive error increases further still.

@@

In this short example, we have shown that the implicit comparisons performed during the forensic analysis of wire cuts have the potential to vastly increase the overall chance that at least one false positive error occurs.
While often a forensic conclusion is presented as a single decision, underlying that decision are many more comparisons which are not discussed or reported upon.
This omission is not necessarily the result of malice; it is the result of a protocol which focuses on finding the best possible match between two items and then evaluating that match.

Our example is the simplest possible case for a wire cut analysis, but the conclusions apply to many other situations where we make multiple comparisons against a set of accumulated information, either in a database or in a series of test samples created during the examination process.
As a result, it is critically important that forensic science grapple with this multiple comparison problem and modify lab procedures and testimony accordingly.
We have three primary suggestions for improvements targeted at making the multiple comparisons visible to everyone involved in the process of evidence evaluation.

@@

Finally, when databases are used at any stage of the forensic evidence evaluation process (from suitability assessment and triage to reports which will be used at trial), the number of database items searched and the number of results resturned must be reported. Furthermore, the number of results used for futher manual comparison should also be reported.
This will help make the multiple comparison issue visible for everyone involved in evaluating the forensic evidence, from examiners themselves to jurors and judges.

We believe that the multiple comparison problems we have discussed here can be overcome with research and changes in evidence assessment procedures, but the first step is making the number of comparisons performed more visible to everyone involved in the process.

>>>>

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor} % colors
\newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
\newcommand{\hh}[1]{{\textcolor{ForestGreen}{#1}}}
\newcommand{\ac}[1]{{\textcolor{Purple}{#1}}}
\templatetype{pnasbriefreport}
%\templatetype{pnasbriefreport} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\title{Mirror, mirror on the wall. Which's the best match of them all?}

@@

\begin{abstract}

\ac{When wires are cut, the tool produces striations on the cut surfaced}; as in other forms of toolmark analysis, these striae are used to connect the wire to the tool that was used \ac{in the cutting process. Here, we argue that the practice} of comparing two wire cut surfaces introduces complexities not present in better-investigated forensic examination  of toolmars such as those observed on bullets, as wire comparisons inherently require multiple distinct comparisons, increasing the expected false positive rate. We call attention to the multiple comparison problem in wire examination and relate it to other situations in forensics that involve multiple comparisons, such as database searches.
\end{abstract}

@@

\dropcap{I}n forensic \ac{evaluations}, a single conclusion often \ac{relies} on  many comparisons, either implicitly or explicitly.
Multiple comparisons arise persistently when developing statistical methods to address scientific problems \citep{benjaminiControllingFalseDiscovery1995}, and can significantly increase the probability of false "discoveries".  Yet, this potentially significant issue is often ignored.  \ac{Now that vast databases and efficient algorithms are routinely used in forensic evaluations to find "matches" to crime scene items, the problems of close non-matches\citep{pcast}, and of the erosion of confidence due to multiple comparisons, become critically important.}
%Researchers have been focusing on building up databases to develop algorithms for objective evidence comparisons.
%\svp{Then, the algorithms facilitate} searches across (vast) databases, reporting the best $N$ matches to a particular piece of evidence.
%This raises the critically important problem of .

@@

A similar concern was raised in the past with regard to DNA \citep{thompson2003} and latent print evaluations  \citep{koehler2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid train bombing case was that the large size of the IAFIS database used to search for similar prints made it possible to locate `unusually' close non-matches.
\ac{The probability of finding  close non-matches for an item of evidence is directly proportional to the size of the database available for searching;} false "matches" occur more frequently as databases increase in size and algorithms become more powerful. 
% In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.

@@

\svp{Compounding this issue,} the use of novel algorithms typically results in a large number of comparisons that may not obvious to the user.
For example, the cross-correlation function\citep{vorburgerApplicationsCrosscorrelationFunctions2011} was one of the first measures proposed for quantifying the similarity  between two patterns in response to the \ac{ 2009 NRC} report \citep{nas2009}, and continues to be used in many pattern searching algorithms to find the best alignment between two images and also to quantify their overall similarity.
Finding the best alignment often consists in sliding one surfaceacross the whole length (for one-dimensional patterns, such as striations) or area (for two dimensional sources, such as impression marks) of the other item while keeping track of the value of a similarity measure.
This mirrors the forensic examination process, where examiners visually rotate or align two surfaces under comparison microscopes.
In order to avoid \ac{problematic} false accusations and a further erosion of the public's trust in science, it is important to address the problem of multiple comparisons by controlling their effect on false discovery rates.

Here, we consider the multiple comparisons problem that arises from a relatively simple toolmark examination: matching a cut wire to a wire-cutting tool.
We describe the comparison approach, estimate the (minimal) number of comparisons that are needed to carry out the examination, and discuss how the false discovery rate changes with the number of comparisons involved, using error rates derived from published black-box studies.

@@

A forensics examiner tasked with determining whether a wire in evidence was cut by a specific tool will create one or more blade cuts \ac{using the putative tool,} which can be compared to the cut surface of the wire.
These cuts are made in a sheet of material similar to the wire's composition, and may be performed at multiple angles, as the angle of the tool to the substrate can affect which striations are recorded on the substrate surface.
The blade cuts will then be compared to the wire under a comparison microscope, though eventually, automatic comparison algorithms may also be validated for lab use.
Each side of each blade cut will be compared to each side of the wire; depending on the tool design, there can be between two and four cutting surfaces in contact with the substrate.

@@

In order to calculate the number of possible comparisons to be carried out in the course of the examination, we define $\ell$ to be the length of the blade cut, and $d$ to be the diameter of the wire. Without loss of generality, we assume that the wire is fully covered with striations suitable for comparison; if this is not the case, we adjust the value of $d$.
\svp{An illustration of the sliding comparison process is shown in \Cref{fig:wire-blade}.} Imagine that you start from the left end of the blade and move the wire surface \ac{$d$ units at a time} along the blade.
At minimum, there must be $\ell/d$ comparisons in order to assess whether one side of the blade cut matches one side of the wire; in this case, the comparisons are independent of each other (conditional on striation patterns) because \ac{each comparison involves different surfaces.}
%no overlapping data is used.
Of course, this overlooks the possibility of partial matches and assumes perfect alignment between the diameter of the wire and the portion of the blade used to cut the wire, which is unrealistic.

@@

At a maximum, both the blade and the wire are either digitally scanned at resolution $r$ mm, or visually examined using a microscope with a digital resolution that can be expressed as $r$ equivalent to the digital scan.
In this case, there may be as many as $\ell/r - d/r + 1$ comparisons performed in order to find the optimal alignment between the two samples.
These comparisons are \ac{no longer independent}, as each sequential comparison shares much of the same data with the previous and next comparisons.
% ; such dependency could be expressed via autocorrelation, but we will defer that derivation to a later paper.
\svp{For simplicity}, let us consider the number of comparisons to lie somewhere between \svp{these two estimates}.

\ac{Finally}, we must consider the number of surfaces which must be compared: the wire may have between one and two sets of striae (depending on tool configuration) and there may be between 2 and 4 different blade cut surfaces to examine.
This results in a multiplier of between 2 and 8 comparisons to be conducted to compare the striations on the wire to the striations on the blade cuts.

@@

Let us consider a wire-cutting tool with a 1.5 cm razor blade that meets a cast surface (one such tool is shown in \Cref{fig:tool-pic}); the wire is held against this rectangular cast surface as the blade is pushed into the wire, splitting it in two.
This is a minimal scenario - the wire will acquire striations from one side of the blade, while the blade itself has two cutting edges, which we will call side A and side B.
The blade cuts of a sheet of aluminum that is 1.5 cm in width thus produce two striated edges corresponding to side A and side B which can be compared to other cuts to assess similarity.

@@

In this example, $\ell = \Sexpr{ell} mm$, $d = \Sexpr{2} mm$, and the minimal number of comparisons between the wire and one blade cut is $\ell/d = \Sexpr{ncomp_min}$.
As there are two blade cuts (side A and side B), the minimal number of comparisons overall is \Sexpr{ncomp_min*2}, and these comparisons are \ac{non-overlapping and} independent.

If the blade cuts and the wire edge are scanned at a resolution of $\Sexpr{res*1000} \mu m$, the resulting digital files will require \svp{approximately $\Sexpr{format(round(ncomp_max/1000)*1000, big.mark=',')}$ comparisons per blade cut; $\Sexpr{format(round(ncomp_max/1000)*2000, big.mark=',')}$ comparisons overall}.
These comparisons are required in order to find the optimal alignment between the wire and the blade cut; they are implicit in the calculation of cross-correlation which is the first \ac{and often} the only step used to objectively assess the similarity between striated evidence such as bullets, aperture shear, and firing pin impressions.
This problem is not unique to algorithms; an examiner would need to physically align the wire and the blade cut by searching along the length of the cut to visually match striations, performing the same process physically that the algorithm performs computationally.
While these sequential comparisons are highly autocorrelated, and we cannot assume sequential independence when calculating the probability of an error, they serve as an upper bound on the number of comparisons which could be performed.

@@

There are \ac{at least }two \ac{contributors} to a false positive rate: coincidental matches (that is, two pieces of evidence that happen to have similar characteristics but are not from the same source) and human/technical failures \citep[p 50]{pcast}.
In objective disciplines with matching rules, such as DNA, these sources can be distinguished, and when coincidental match rates are very low, human/technical failures make up a large component of the error rate.
However, in toolmark examination, we do not have an objective matching rule; examiners testify based on subjective, individual rules for how much similarity is enough for an identification.
As a result, we cannot separate coincidental match rates from human/technical failures.
<<fpr, include = F>>=
errors <- c(20, 56, 1)
knm <- c(2842, 774, 220)

@@

%Compounding this problem, o
Open-set studies of striated comparisons (bullets and firing pin impressions) \citep{bajic2020, mattijssen2021,best2022} suggest \svp{that a starting point for estimating the} false positive rate for these comparisons is between 0.0045 \citep{best2022} and 0.072 \citep{mattijssen2021}; pooling data from these three studies yields a false positive rate of \Sexpr{sprintf("%.2f", fpr)}.

If we begin by considering the multiple comparison problem relative to the $\ell/d$ independent comparisons between a blade cut and a wire, we can compute the overall false positive rate for all comparisons using $r$, the false positive rate for one comparison, and simple probability \ac{calculations}. Let $$F_n:=\{\text{at least one false pos. in }n\text{ disjoint comparisons}\}.$$ Then, $P(F_1) = r$, $P(\overline{F_1}) = 1-r$, $P(F_n) = [1-r]^n$, and $P(\overline{F_n}) = 1 - \left[P(\overline{F_1})\right]^n$.
% Using this relationship between $F_n$ and the false positive rate $r$, we can determine what $r$ must be in order to limit $P(F_n)$ to an acceptable level by solving for $r$: $r = 1 - \left[1 - P(F_n)\right]^{1/n}$.
\svp{\Cref{fig:Accuracy} shows $P(\overline{F_n})$ on the y-axis; if we set 90\% as the acceptable} \ac{examination-wide false positive rate (FPR)}, we can make 2 comparisons when the single-comparison FPR is 0.05 and 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, we can conduct approximately 5 comparisons \ac{in the course of an examination without exceeding the examination-wide FPR of 10\%.}

\svp{It is clear that under these constraints, the} accuracy of the \ac{forensic evaluation that involves multiple comparisons} between a wire and a tool \ac{is likely to be low}, as the number of candidate alignments that must be examined is too high.
Even the most innocuous example we could come up with (small blade, only 2 cutting surfaces, and a relatively large wire) involved a minimum of \Sexpr{2*ncomp_min} completely independent comparisons.
As a result, \ac{findings from}  wire comparisons made under current protocols (using error rates recently published in the forensics literature) \ac{are probably not} reliable enough to be presented at trial.
When we then consider that examiners would make cuts at multiple angles \citep{baikerToolmarkVariabilityQuality2015}, increasing the number of comparisons even in the simple case we have presented here, the probability of a false positive error increases further still.

@@

\ac{Forensic practitioners often report the findings from their examinations in the form of a categorical conclusion reflecting a single decision. This can be misleading when the one decision relies on multiple comparisons which are not individually presented in reports or testimony.} In this short contribution, we have shown that the implicit comparisons performed during the forensic analysis of wire cuts have the potential to vastly increase the overall chance that at least one false positive error occurs.
%While often a forensic conclusion is presented as a single decision, underlying that decision are many more comparisons which are not discussed or reported upon.
\ac{Omission of the underlying} details is not necessarily \ac{due to} malice; rather, it results from protocols which focus on finding the best possible match between two items and then evaluating that match, \ac{and also from lack of familiarity with basic statistical ideas.}

In our example \ac{we highlight a simple} case where a wire \ac{ is cut using a two-sided blade}, but the findings apply to many other situations where \ac{a forensic evaluation involves} multiple comparisons against a set of accumulated information. \ac{Examples include a database search or a situation similar to the example where multiple comparisons of evidence against reference samples are conducted.}
%either in a database or in a series of test samples created during the examination process.
As a result, it is critically important that forensic \ac{practitioners become aware of the impact of carrying out multiple comparisons on their final conclusions}
%science grapple with this multiple comparison problem and 
and that they modify lab procedures and testimony accordingly. \ac{We suggest three strategies to improve transparency of forensic examinations and to produce more reliable estimates of examination-wide error rates.}
%We have three primary suggestions for improvements targeted at making the multiple comparisons visible to everyone involved in the process of evidence evaluation.

@@

Finally, when databases are used at any stage of the forensic evidence evaluation process (from suitability assessment and triage to reports which will be used at trial), the number of database items searched and the number of results returned must be reported. Furthermore, the number of results used for futher manual comparison should also be reported. For example, if a firearms examiner searches a local NIBIN database with 1000 entries, requests the 20 closest matches to her evidence, and then carries out a physical examination of five exemplars from the list of 20, all of those values should be clearly reported to enable calculation of the potential FPR.  
This will help make the multiple comparison issue visible for everyone involved in evaluating the forensic evidence, from examiners themselves to jurors and judges.

%We believe that the multiple comparison problems we have discussed here can be overcome with research and changes in evidence assessment procedures, but the first step is making the number of comparisons performed more visible to everyone involved in the process.
